\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Yuanxuan}
\familyname{Wang}
\title{Curriculum Vitae}
\mobile{+86 18612345677}
\email{donotsend@me.com}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{2010--Present}{MS in System Software, Supervisor: Haibo Chen}{Software School, Fudan University}{expected 2013}{}{}
\cventry{2006--2010}{BS in Software Engineering}{Software School, Fudan University}{}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

\section{Internship}
\cventry{2012}{Summer Analyst at Morgan Stanley}{E-Trading Infrastructure Department}{}{}{Designed and implemented a BitTorrent based system to speed up trading data precache}
\cventry{2011}{Summer internship at EMC Research Shanghai}{}{}{}{Researched on I/O side channel attack in a share-host environment}

\section{Community}
\cventry{Blog}{\url{blog.yxwang.me}}{My blog (Chinese)}{}{}{}
\cventry{Stack Overflow}{\url{stackoverflow.com/users/111896/zellux}}{Reputation top 4\%}{}{}{}
\cventry{GitHub}{\url{github.com/zellux}}{}{}{}{}

\section{Project Experience}
%% \subsection{Research Projects}

\cventry{2011--present}
{Tangcha Project}
{iOS, Ruby on Rails}
{Startup Project}{}
{
Tangcha is a startup project, aimed at providing the best online
Chinese ebook store for readers. I have been working as a part-time
developer in Tangcha, and responsible for designing and implementing
most functions of the back-end server, including purchasing interfaces
for mobile phones and tablets, user authorization, transaction
validation, third-party storage integration, synchronization service,
dashboard for publishers and administrators, server configuration, and
etc.
}

\vspace*{0.2\baselineskip}
\cventry{2011--2012}
{ReDroid}
{Android}
{Research Project}{}
{Working with Jinchen Han, Chen Tan, Prof. Haibo Chen and Prof. Binyu Zang. \\
ReDroid is an event-centric record and replay framework that targets
smartphone platforms. We ensure its replayability as well as low
recording overhead by optimization techniques including fine-grained
UI-event based recording, coarse-grained data based recording,
intertwined replay, and system call interception to handle some low
level undeterminism. I was the major contributor of this project and the paper has been submitted to ASPLOS '13.
}

\vspace*{0.2\baselineskip}
\cventry{2009--2011}
{Cerberus}
{Xen, Linux Kernel}
{Research Project}{}
{Working with Xiang Song, Rong Chen, Prof. Haibo Chen and Prof. Binyu Zang. \\
Cerberus aims at improving application scalability on many-core in a
backward-compatibility way. To mitigate contention on shared data
structures within OS kernels, Cerberus clusters multiple commodity
operating systems atop a VMM. It achieves up to 3.49x Apache httpd
throughput compared to vanilla Linux on a 16-core machine.
}

%% \cventry{2011--present}
%% {AlgoTrading}
%% {Go, Java}
%% {}{}
%% {An analyzing tool for offline trading strategy emulating. Data are parsed from TongDaXin stock trading software, I emulated and evaluated several trading strategies based on this project.}

%% \cventry{2008}{GPGPU Optimization}{C++, CTM IL}{}{}{Research on GPGPU program optimization and platform features}

%% \subsection{Course Projects}
%% \cventry{2008}{Compiler for Tiger Language}{C, Flex, Bison}{}{}{Project for the course Compilers}

%% \subsection{Other Projects}
%% \vspace*{0.2\baselineskip}
\cventry{2010}
{ForceField}
{Python, ANTLR}
{Independent Project}{}
{In collaboration with Menghua Xiao. \\
We designed a scripting language named ForceField, and implemented an
interpreter for it using Python and ANTLR. To simplify debugging
ForceField scripts, we also developed an online debugging service,
with features like single stepping and variable watching available
through web interface.
}

\vspace*{0.2\baselineskip}
\cventry{2010}
{AppFlight for Android}
{Android}
{Startup Project}{}
{
A user customizable application framework. Users define contents and
layout style in a web CMS, we then render those contents on mobile
applications.
}

%% \cventry{2010}
%% {Computer System Engineering Teaching Assistant}{}{}{}
%% {}

\vspace*{0.2\baselineskip}
\cventry{2009}
{Nexus}
{C, Assembly}
{Independent Project}{}
{
An exokernel-like operating system, based on MIT Course 6.828.
}

%% \cventry{2009}
%% {Operating System Teaching Assistant}{}{}{}{}

\vspace*{0.2\baselineskip}
\cventry{2009}
{Reading Progress Tracker}
{Python, Django, Google App Engine}
{Independent Project}{}
{
A web application to help user track everyday reading progress. The reading list is synced with douban.com.
}

% \cventry{2008}{Koprulu}{C, Assembly}{}{}{A simple multi-tasking preemptive OS kernel, based on CMU 15-410 lab.}
%% \cventry{2008}{Distributed IRC Server}{C}{}{}{Project for the course Networking}

\vspace*{0.2\baselineskip}
\cventry{2008}
{Koprulu}
{C, Assembly}
{Course Project}{}
{
A simple multi-tasking preemptive OS kernel, based on CMU 15-410 lab.
}

\vspace*{0.2\baselineskip}
\cventry{2008}
{GPA Calculator for Fudan Students}
{Python, wxWidgets}
{Independent Project}{}
{
A desktop application which fetches and parses course grades from web
pages, and calculates GPA based on parsing result. It had been
downloaded over 6000 times in one year.
}

% \cventry{2007}{Collaborative Multi-client Drawing System}{Java, RMI}{}{}{Project for Object-Oriented Programming course.}
%% \cventry{2008}{Succour Administration System for Changzheng Community}{Java, JSP}{}{}{A simple web-based succour management system}
%% \cventry{2007}{Train Ticket Booking System for Fudan University}{Java, JSP}{}{}{My first out-sourcing project}

\section{Publications}

\cventry{2012}
{\textbf{Yuanxuan Wang}\textnormal{, Jincheng Han, Haibo Chen, Binyu Zang}}
{ReDroid: Fast Malware Recovery on Smartphones with Intertwined Replay}{In IPADS Technique Report}
{}{}{}

\cventry{2011}
{\textnormal{Xiang Song, Haibo Chen, Rong Chen,} \textbf{Yuanxuan Wang}\textnormal{, Binyu Zang}}
{A Case for Scaling Applications to Many-core Platforms with OS Clustering}
{In 2011 ACM SIGOPS European Conference on Computer Systems (Eurosys'2011)}
{}{}{}

\section{Awards}
\cventry{2012}{Most Creative Award of Morgan Stanley Summer Intern Team Project}{}{}{}{}
\cventry{2010}{First Prize in SAP Dashboard Competition 2010}{}{}{}{}
\cventry{2010}{First Prize in Cloud Computing in Shanda Campus Master Innovation Contest}{}{}{}{}
\cventry{2010}{First Grade Scholarship for Graduates}{}{}{}{}
% \cventry{2009}{Third Grade People's Scholarship}{}{}{}{}
%% \cventry{2007, 2008}{Second Grade Scholarship for Undergraduates}{}{}{}{}
\cventry{2007}{First Place in Zhangjiang Cup, Dota Allstars}{}{}{}{}
\cventry{2006, 2008}{Second Place in Fudan E-sports Game, Starcraft}{}{}{}{}
% \cventry{2006}{Third Prize in Fudan Technology Contest}{}{}{}{}
\cventry{2005, 2004}{First Prize in National Olympiad in Informatics in Provinces}{}{}{}{}

\section{Skills}
\cventry{Languages}{Ruby = C = Java > Python > C++}{}{}{}{}
\cventry{Kernels}{Linux, Xen, Android}{}{}{}{}
%% \cventry{Application Dev}{Ruby on Rails, iOS development}{}{}{}{}
\cventry{English}{CET-6 593}{fluent in spoken and written English, also a TED translator}{}{}{}
\cventry{Games}{Starcraft 2 (Master League)}{}{}{}{}

% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
